Equivalent Income Stuff - Energy Crisis Plots

### 2024-01-05 minos/outcomes/EI_allScen_Plots.Rmd
Additions to the EI plotting script

income_equivinc_percent_change_batch(base.batch, int.batch, int.name, group.var = 'income.quint')
```

@@

S7_ordinal_pathway_batch(base.batch, energy.batch, 'Energy Crisis', 'S7_housing_quality')
```

@@

```{r}
S7_pathway_change_byGroup(base.batch, energy.batch, group.var = 'income.quint', var = 'S7_housing_quality')
S7_pathway_change_byGroup(base.batch, energy.batch, group.var = 'income.quint', var = 'S7_neighbourhood_safety')
S7_pathway_change_byGroup(base.batch, energy.batch, group.var = 'income.quint', var = 'S7_physical_health')
S7_pathway_change_byGroup(base.batch, energy.batch, group.var = 'income.quint', var = 'S7_mental_health')
S7_pathway_change_byGroup(base.batch, energy.batch, group.var = 'income.quint', var = 'loneliness')
```

@@

```{r}
S7_cumulative_pathwayChange_byGroup(base.batch, energy.batch, group.var = 'income.quint', var = 'S7_housing_quality')
S7_cumulative_pathwayChange_byGroup(base.batch, energy.batch, group.var = 'income.quint', var = 'S7_neighbourhood_safety')
S7_cumulative_pathwayChange_byGroup(base.batch, energy.batch, group.var = 'income.quint', var = 'S7_physical_health')
S7_cumulative_pathwayChange_byGroup(base.batch, energy.batch, group.var = 'income.quint', var = 'S7_mental_health')
S7_cumulative_pathwayChange_byGroup(base.batch, energy.batch, group.var = 'income.quint', var = 'loneliness')
```

@@

```{r}
S7_cumulative_pathwayChange_byGroup(base.batch, energy.batch, group.var = 'age.group', var = 'S7_housing_quality')
S7_cumulative_pathwayChange_byGroup(base.batch, energy.batch, group.var = 'age.group', var = 'S7_neighbourhood_safety')
S7_cumulative_pathwayChange_byGroup(base.batch, energy.batch, group.var = 'age.group', var = 'S7_physical_health')
S7_cumulative_pathwayChange_byGroup(base.batch, energy.batch, group.var = 'age.group', var = 'S7_mental_health')
S7_cumulative_pathwayChange_byGroup(base.batch, energy.batch, group.var = 'age.group', var = 'loneliness')
```

@@

```{r}
group.var <- 'income.quint'
var <- 'S7_mental_health'

base.sub <- base.batch %>%
  select(pidp, time, run_id, all_of(group.var), all_of(var)) %>%
  rename(Baseline_var = S7_mental_health,
         Baseline_income.quint = income.quint)

int.sub <- energy.batch %>%
  select(pidp, time, run_id, all_of(group.var), all_of(var)) %>%
  rename(Intervention_var = S7_mental_health,
         Intervention_income.quint = income.quint)

#combined <- rbind(base.sub, int.sub)

@@

```{r}
# move further analysis here so we don't have to do that expensive merge every time
merged2 <- merged %>%
  mutate(varChange = Intervention_var - Baseline_var,
         effect = case_when(varChange > 0 ~ "Positive",
                            varChange < 0 ~ "Negative",
                            varChange == 0 ~ "No_Change")) %>%
  select(-Baseline_var, -Intervention_var, -Intervention_income.quint, -varChange) %>%
  rename(income.quint = Baseline_income.quint) %>%
  group_by(time, run_id, .data[[group.var]], effect) %>%
  count() %>%
  group_by(time, run_id, .data[[group.var]]) %>%
  mutate(total = sum(n),
         effect_prop = n / total) %>%
  select(-n, -total) %>%
  group_by(time, .data[[group.var]], effect) %>%
  summarise(effect_prop = mean(effect_prop)) %>%
  pivot_wider(names_from = 'effect',
              values_from = 'effect_prop') %>%
  mutate(change = Positive - Negative) %>%
  select(-Positive, -Negative, -No_Change, -time) %>%
  group_by(.data[[group.var]]) %>%
  summarise(change = sum(change))

ggplot(data = merged2, aes(x = income.quint, y = change)) +
  geom_col()
```

@@

```{r}
simplified_component_change(base.batch, energy.batch, group.var = 'income.quint', var = 'S7_housing_quality', print = TRUE)
simplified_component_change(base.batch, energy.batch, group.var = 'income.quint', var = 'S7_neighbourhood_safety', print = TRUE)
simplified_component_change(base.batch, energy.batch, group.var = 'income.quint', var = 'S7_mental_health', print = TRUE)
simplified_component_change(base.batch, energy.batch, group.var = 'income.quint', var = 'S7_physical_health', print = TRUE)
simplified_component_change(base.batch, energy.batch, group.var = 'income.quint', var = 'loneliness', print = TRUE)
```

@@

df <- simplified_component_change(base.batch, energy.batch, group.var = 'income.quint', var = 'S7_housing_quality')
colnames(df) <- c('Income_Quintile', 'S7_housing_quality')
for (S7_var in varlist) {
  df2 <- simplified_component_change(base.batch, energy.batch, group.var = 'income.quint', var = S7_var)
  colnames(df2) <- c('Income_Quintile', S7_var)
  df <- merge(df, df2, by = c('Income_Quintile'))
}
rm(df2)

ggplot(df2, aes(x = Variable, y = Change, group = Variable, colour = Variable, fill = Variable)) +
  geom_col() +
  facet_wrap(~ Income_Quintile, nrow = 1) +
  theme(legend.position = 'bottom',
        axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank())
```

@@

df <- simplified_component_change_BOXPLOT(base.batch, energy.batch, group.var = 'income.quint', var = 'S7_housing_quality')
colnames(df) <- c('run_id', 'Income_Quintile', 'S7_housing_quality')
for (S7_var in varlist) {
  df2 <- simplified_component_change_BOXPLOT(base.batch, energy.batch, group.var = 'income.quint', var = S7_var)
  colnames(df2) <- c('run_id', 'Income_Quintile', S7_var)
  df <- merge(df, df2, by = c('run_id', 'Income_Quintile'))
}
rm(df2)

@@

ggplot(df2, aes(x = Variable, y = Change, group = Variable, colour = Variable, fill = Variable)) +
  geom_boxplot(notch = FALSE) +
  facet_wrap(~ Income_Quintile, nrow = 1) +
  geom_hline(yintercept = 0, linetype = 'dashed') +
  theme(legend.position = 'bottom',
        axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank())
```

>>>>

income_equivinc_percent_change_batch(base.batch, energy.batch, 'Energy Crisis', group.var = 'income.quint')
income_equivinc_percent_change_batch(base.batch, wage.batch, 'Living Wage', group.var = 'income.quint')
income_equivinc_percent_change_batch(base.batch, child.batch, 'All Child Uplift', group.var = 'income.quint')
income_equivinc_percent_change_batch(base.batch, pov.batch, 'Povety Child Uplift', group.var = 'income.quint')
```

@@

S7_ordinal_pathway_batch(base.batch, energy.batch, 'Energy Crisis', 'S7_housing_quality')
S7_ordinal_pathway_batch(base.batch, wage.batch, 'Living Wage', 'S7_housing_quality')
S7_ordinal_pathway_batch(base.batch, child.batch, 'All Child Uplift', 'S7_housing_quality')
S7_ordinal_pathway_batch(base.batch, pov.batch, 'Poverty Child Uplift', 'S7_housing_quality')
```

@@

```{r}
# S7_pathway_change_byGroup(base.batch, energy.batch, group.var = 'income.quint', var = 'S7_housing_quality')
# S7_pathway_change_byGroup(base.batch, energy.batch, group.var = 'income.quint', var = 'S7_neighbourhood_safety')
# S7_pathway_change_byGroup(base.batch, energy.batch, group.var = 'income.quint', var = 'S7_physical_health')
# S7_pathway_change_byGroup(base.batch, energy.batch, group.var = 'income.quint', var = 'S7_mental_health')
# S7_pathway_change_byGroup(base.batch, energy.batch, group.var = 'income.quint', var = 'loneliness')
```

@@

```{r}
# S7_cumulative_pathwayChange_byGroup(base.batch, energy.batch, group.var = 'income.quint', var = 'S7_housing_quality')
# S7_cumulative_pathwayChange_byGroup(base.batch, energy.batch, group.var = 'income.quint', var = 'S7_neighbourhood_safety')
# S7_cumulative_pathwayChange_byGroup(base.batch, energy.batch, group.var = 'income.quint', var = 'S7_physical_health')
# S7_cumulative_pathwayChange_byGroup(base.batch, energy.batch, group.var = 'income.quint', var = 'S7_mental_health')
# S7_cumulative_pathwayChange_byGroup(base.batch, energy.batch, group.var = 'income.quint', var = 'loneliness')
```

@@

```{r}
# S7_cumulative_pathwayChange_byGroup(base.batch, energy.batch, group.var = 'age.group', var = 'S7_housing_quality')
# S7_cumulative_pathwayChange_byGroup(base.batch, energy.batch, group.var = 'age.group', var = 'S7_neighbourhood_safety')
# S7_cumulative_pathwayChange_byGroup(base.batch, energy.batch, group.var = 'age.group', var = 'S7_physical_health')
# S7_cumulative_pathwayChange_byGroup(base.batch, energy.batch, group.var = 'age.group', var = 'S7_mental_health')
# S7_cumulative_pathwayChange_byGroup(base.batch, energy.batch, group.var = 'age.group', var = 'loneliness')
```

@@

```{r}
# group.var <- 'income.quint'
# var <- 'S7_mental_health'
# 
# base.sub <- base.batch %>%
#   select(pidp, time, run_id, all_of(group.var), all_of(var)) %>%
#   rename(Baseline_var = S7_mental_health,
#          Baseline_income.quint = income.quint)
# 
# int.sub <- energy.batch %>%
#   select(pidp, time, run_id, all_of(group.var), all_of(var)) %>%
#   rename(Intervention_var = S7_mental_health,
#          Intervention_income.quint = income.quint)
# 
# merged <- merge(base.sub, int.sub,
#                 by=c('pidp', 'time', 'run_id'),
#                 all = FALSE)
# 
# #combined <- rbind(base.sub, int.sub)

@@

```{r}
# move further analysis here so we don't have to do that expensive merge every time
# merged2 <- merged %>%
#   mutate(varChange = Intervention_var - Baseline_var,
#          effect = case_when(varChange > 0 ~ "Positive",
#                             varChange < 0 ~ "Negative",
#                             varChange == 0 ~ "No_Change")) %>%
#   select(-Baseline_var, -Intervention_var, -Intervention_income.quint, -varChange) %>%
#   rename(income.quint = Baseline_income.quint) %>%
#   group_by(time, run_id, .data[[group.var]], effect) %>%
#   count() %>%
#   group_by(time, run_id, .data[[group.var]]) %>%
#   mutate(total = sum(n),
#          effect_prop = n / total) %>%
#   select(-n, -total) %>%
#   group_by(time, .data[[group.var]], effect) %>%
#   summarise(effect_prop = mean(effect_prop)) %>%
#   pivot_wider(names_from = 'effect',
#               values_from = 'effect_prop') %>%
#   mutate(change = Positive - Negative) %>%
#   select(-Positive, -Negative, -No_Change, -time) %>%
#   group_by(.data[[group.var]]) %>%
#   summarise(change = sum(change))
# 
# ggplot(data = merged2, aes(x = income.quint, y = change)) +
#   geom_col()
```

@@

```{r}
# simplified_component_change(base.batch, energy.batch, group.var = 'income.quint', var = 'S7_housing_quality', print = TRUE)
# simplified_component_change(base.batch, energy.batch, group.var = 'income.quint', var = 'S7_neighbourhood_safety', print = TRUE)
# simplified_component_change(base.batch, energy.batch, group.var = 'income.quint', var = 'S7_mental_health', print = TRUE)
# simplified_component_change(base.batch, energy.batch, group.var = 'income.quint', var = 'S7_physical_health', print = TRUE)
# simplified_component_change(base.batch, energy.batch, group.var = 'income.quint', var = 'loneliness', print = TRUE)
```

@@

sccb_all_vars <- function(base.batch, int.batch, group.var, varlist) {
  df <- simplified_component_change(base.batch, energy.batch, group.var = 'income.quint', var = 'S7_housing_quality')
  colnames(df) <- c('Income_Quintile', 'S7_housing_quality')
  for (S7_var in varlist) {
    df2 <- simplified_component_change(base.batch, energy.batch, group.var = 'income.quint', var = S7_var)
    colnames(df2) <- c('Income_Quintile', S7_var)
    df <- merge(df, df2, by = c('Income_Quintile'))
  }
  rm(df2)

  # finally pivot_longer for ggplot and facet_wrap to take over
  df2 <- df %>%
    pivot_longer(cols = S7_housing_quality:S7_mental_health,
                 names_to = 'Variable',
                 values_to = 'Change')
  p1 <- ggplot(df2, aes(x = Variable, y = Change, group = Variable, colour = Variable, fill = Variable)) +
  geom_col() +
  facet_wrap(~ Income_Quintile, nrow = 1) +
  theme(legend.position = 'bottom',
        axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank())
  print(p1)
}

sccb_all_vars(base.batch, energy.batch, group.var = 'income.quint', varlist = varlist)
sccb_all_vars(base.batch, wage.batch, group.var = 'income.quint', varlist = varlist)
sccb_all_vars(base.batch, child.batch, group.var = 'income.quint', varlist = varlist)
sccb_all_vars(base.batch, pov.batch, group.var = 'income.quint', varlist = varlist)

@@

sccb_all_vars_BOXPLOT <- function(base.batch, int.batch, group.var, varlist) {
  df <- simplified_component_change_BOXPLOT(base.batch, energy.batch, group.var = group.var, var = 'S7_housing_quality')
  colnames(df) <- c('run_id', 'Income_Quintile', 'S7_housing_quality')
  for (S7_var in varlist) {
    df2 <- simplified_component_change_BOXPLOT(base.batch, energy.batch, group.var = 'income.quint', var = S7_var)
    colnames(df2) <- c('run_id', 'Income_Quintile', S7_var)
    df <- merge(df, df2, by = c('run_id', 'Income_Quintile'))
  }
  rm(df2)

@@

  p1 <- ggplot(df2, aes(x = Variable, y = Change, group = Variable, colour = Variable, fill = Variable)) +
    geom_boxplot(notch = FALSE) +
    facet_wrap(~ Income_Quintile, nrow = 1) +
    geom_hline(yintercept = 0, linetype = 'dashed') +
    theme(legend.position = 'bottom',
          axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank())
  print(p1)
}

sccb_all_vars_BOXPLOT(base.batch, energy.batch, group.var = 'income.quint', varlist = varlist)
sccb_all_vars_BOXPLOT(base.batch, wage.batch, group.var = 'income.quint', varlist = varlist)
sccb_all_vars_BOXPLOT(base.batch, child.batch, group.var = 'income.quint', varlist = varlist)
sccb_all_vars_BOXPLOT(base.batch, pov.batch, group.var = 'income.quint', varlist = varlist)
```
